---
title: "Self-training classification round 4"
author: "Siri Frisli"
output:
  html_notebook:
    toc: yes
    number_sections: yes
    toc_depth: '3'
    toc_float:
      collapsed: no
    df_print: paged
---

```{r setup, include = FALSE}
packages <- c("tidyverse", "tidymodels", "readxl", "ROSE", "recipes", "textrecipes",
              "e1071", "caret", "glmnet", "spacyr", "textdata", "xgboost", "data.table")
 
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package,
                     dependencies = TRUE,
                     repos='http://cran.us.r-project.org')
  }
}

for (package in packages){
  library(package, character.only = TRUE)
}

knitr::opts_chunk$set(echo = TRUE)
```

Loading the data, this has already gone through one round of classification
```{r}
covid <- readRDS("E:/Data/Training samples/misinformation_class_3.RDS")
stopwords <- read_xlsx("~/INORK/Processing/stopwords.xlsx")
custom_words <- stopwords |>
  pull(word)
```

Creating the splits:
```{r}
set.seed(1234)
covid_split <- initial_split(covid, prop = 0.8, strata = label)
train <- training(covid_split)
test <- testing(covid_split)
```

Initializing spacyr environment and loading the pre-trained word embeddings (norwegian bokmål)
```{r}
spacy_initialize(model = "nb_core_news_sm")
no_we <- fread("~/SVM_ST/model_1.txt", 
                    skip = 1, header = FALSE, sep = " ", quote = "", encoding = "UTF-8")
no_we <- no_we |>
  as_tibble()
```

# Recipe
Calculate and add weights 
```{r}
341593/(table(train$label)[1] * 2)
341593/(table(train$label)[2] * 2)
```

```{r}
train <- train |>
  mutate(case_wts = ifelse(label == "misinfo", 3.704833, 0.5780072),
         case_wts = importance_weights(case_wts))
```

```{r}
model_recipe <- recipe(label~tweet+case_wts, data = train) |>
  step_tokenize(tweet, engine = "spacyr") |>
  step_stopwords(tweet, language = "no", keep = FALSE, 
                 stopword_source = "snowball", 
                 custom_stopword_source = custom_words) |>
  step_lemma(tweet) |>
  step_word_embeddings(tweet, embeddings = no_we) |>
  step_normalize(all_numeric_predictors())

model_recipe
```

# Logistic regression
```{r}
lr_spec <- logistic_reg(penalty = tune(), mixture = 1) |>
  set_mode("classification") |>
  set_engine("glmnet")
```

```{r}
lr_workf <- workflow() |>
  add_model(lr_spec) |>
  add_recipe(model_recipe) |>
  add_case_weights(case_wts)
lr_workf
```

```{r}
set.seed(8008)
folds <- vfold_cv(train, strata = label, v = 5, repeats = 2)
grid <- tibble(penalty = 10^seq(-3, 0, length.out = 20))
cls_metric <- metric_set(yardstick::precision, yardstick::recall, yardstick::f_meas)
```

```{r}
set.seed(1)
lr_res <- lr_workf |>
  tune_grid(resamples = folds, grid = grid, metrics = cls_metric)
```

```{r}
lr_params <- select_best(lr_res, metric = "f_meas")

lr_final_workf <- lr_workf |>
  finalize_workflow(lr_params)
```

```{r}
set.seed(2)
lr_final_fit <- fit(lr_final_workf, train)

lr_preds <- test |>
  bind_cols(predict(lr_final_fit, test))

cm_lr <- confusionMatrix(table(test$label, lr_preds$.pred_class)) 
cm_lr$byClass["F1"] # 0.9963246  
cm_lr$byClass["Precision"] # 0.9995662  
cm_lr$byClass["Recall"] # 0.993104  
```
```{r}
# saveRDS(lr_final_fit, "~/SVM_ST/log_reg_round4.RDS")
```

# Loading and preprocessing full dataset
```{r}
covid_df <- readRDS("E:/Data/covid_relevant_nort_domain.RDS")

# match <- subset(covid, (covid$id %in% covid_df$id))
covid_df <- covid_df |>
 # anti_join(match, by = "id") |>
  rename(tweet = text)
```

```{r}
# covid_df <- covid_df |>
#   sample_n(300000, seed = 700)
```

```{r}
removeURL <- function(tweet) {
  return(gsub("http\\S+", "", tweet))
}

removeUsernames <- function(tweet) {
  return(gsub("@[a-z,A-Z,_]*[0-9]*[a-z,A-Z,_]*[0-9]*", "", tweet))
}

covid_df$tweet <- apply(covid_df["tweet"], 1, removeURL)
covid_df$tweet <- apply(covid_df["tweet"], 1, removeUsernames)

covid_df$tweet <- tolower(covid_df$tweet)
covid_df$tweet <- gsub("[[:punct:]]", " ", covid_df$tweet)
# covid_df$tweet <- str_replace_all(covid_df$tweet, "[0-9]", "")
```

## Logistic regression on the new sample
```{r}
set.seed(123)
lr_preds_all <- covid_df |>
  bind_cols(predict(lr_final_fit, covid_df, type = "prob"))
```

```{r}
lr_preds_all_filtered <- lr_preds_all |>
  filter(.pred_misinfo > 0.9 | .pred_non.misinfo > 0.9)
```

```{r}
lr_preds_all_filtered_label <- lr_preds_all_filtered |>
  mutate(label = case_when(
    .pred_misinfo > 0.9 ~ "misinfo",
    .pred_non.misinfo > 0.9 ~ "non.misinfo"
  ))
```

```{r}
lr_preds_all_filtered_label <- lr_preds_all_filtered_label |>
  select(tweet, label, id)
```

```{r}
lr_preds_all_filtered_label |>
  count(label)
```

Merging the two datasets and saving it as a new training sample
```{r}
# match <- subset(covid, (covid$id %in% lr_preds_all_filtered_label$id))

covid_predicted <- full_join(lr_preds_all_filtered_label, covid, by = "id") |>
  mutate(label = coalesce(label.x, label.y),
         tweet = coalesce(tweet.x, tweet.y)) |>
  select(tweet, label, id)

covid_predicted |>
  count(label)
```

```{r}
saveRDS(covid_predicted, "E:/Data/Training samples/misinformation_class_4.RDS")
```