---
title: "Manually labelled sample + links with word embeddings"
author: "Siri Frisli"
output:
  html_notebook:
    toc: yes
    number_sections: yes
    toc_depth: '3'
    toc_float:
      collapsed: no
    df_print: paged
---

```{r setup, include = FALSE}
packages <- c("tidyverse", "tidymodels", "readxl", "ROSE", "recipes", "textrecipes",
              "e1071", "caret", "glmnet", "spacyr", "textdata", "xgboost")
 
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package,
                     dependencies = TRUE,
                     repos='http://cran.us.r-project.org')
  }
}

for (package in packages){
  library(package, character.only = TRUE)
}

knitr::opts_chunk$set(echo = TRUE)
```

# Loading and preprocessing data
```{r}
covid <- read_xlsx("D:/Data/Training samples/misinformation_labeled.xlsx")
covid_links <- readRDS("D:/Data/covid_misinfo_links_only.RDS")

stopwords <- read_xlsx("~/INORK/INORK_R/Processing/stopwords.xlsx")
custom_words <- stopwords |>
  pull(word)
```

Checking the balance between classes in the manually labelled sample
```{r}
covid |>
  count(label)
```
Need to extract about 900 observations from the link sample

```{r}
covid_links <- covid_links |>
  select(-dom_url) |>
  sample_n(900)

covid <- covid |>
  select(-c(claim, description, fact_check, date))

covid_full <- rbind(covid_links, covid)
covid <- covid_full

covid <- covid |>
  select(tweet = text, label, id)

covid$label <- case_when(
  covid$label == 0 ~ "non.misinfo",
  covid$label == 1 ~ "misinfo"
)
```

```{r}
covid |>
  count(label)
```
Now the classes are balanced

```{r}
removeURL <- function(tweet) {
  return(gsub("http\\S+", "", tweet))
}

removeUsernames <- function(tweet) {
  return(gsub("@[a-z,A-Z,_]*[0-9]*[a-z,A-Z,_]*[0-9]*", "", tweet))
}

covid$tweet <- apply(covid["tweet"], 1, removeURL)
covid$tweet <- apply(covid["tweet"], 1, removeUsernames)

covid$label <- as.factor(covid$label) # Outcome variable needs to be factor
covid$tweet <- tolower(covid$tweet)
covid$tweet <- gsub("[[:punct:]]", " ", covid$tweet)
# covid$tweet <- str_replace_all(covid$tweet, "[0-9]", "")

# saveRDS(covid, "D:/Data/manual_links_sample.RDS")
```

```{r}
# covid <- readRDS("D:/Data/manual_links_sample.RDS")
```


The splits:
```{r}
set.seed(1234)
covid_split <- initial_split(covid, prop = 0.8, strata = label)
train <- training(covid_split)
test <- testing(covid_split)
```

Initializing spacyr environment and loading the pre-trained word embeddings (norwegian bokmål)
```{r}
spacy_initialize(model = "nb_core_news_sm")
no_we <- fread("C:/Users/sirifris.ADA/OneDrive - OsloMet/Dokumenter/model.txt", 
                    skip = 1, header = FALSE, sep = " ", quote = "", encoding = "UTF-8")
no_we <- no_we |>
  as_tibble()
```

## Recipe
```{r}
covid_recipe <- recipe(label~tweet, data = train) |>
  step_tokenize(tweet, engine = "spacyr") |>
  step_stopwords(tweet, language = "no", keep = FALSE, 
                 stopword_source = "snowball", 
                 custom_stopword_source = custom_words) |>
  step_lemma(tweet) |>
  step_word_embeddings(tweet, embeddings = no_we) |>
  step_normalize(all_numeric_predictors()) |>
  prep()

new_train <- bake(covid_recipe, new_data = train)
new_test <- bake(covid_recipe, new_data = test)
```

# Model training: SVM
First checking the performance of the default model
```{r}
set.seed(1234)
svm_model <- svm(formula = label~.,
                 data = new_train,
                 type = "C-classification",
                 kernel = "radial",
                 cross = 5,
                 probability = TRUE)
```

```{r}
test_svm <- new_test |>
  bind_cols(predict(svm_model, new_test))

cm_svm_test <- confusionMatrix(table(new_test$label, test_svm$...302)) 
cm_svm_test$byClass["F1"] # 0.8643216  
cm_svm_test$byClass["Precision"] # 0.877551  
cm_svm_test$byClass["Recall"] # 0.8514851  
```

```{r}
new_test |>
  bind_cols(predict(svm_model, new_test)) |>
  conf_mat(truth = label, estimate = ...302) |>
  autoplot(type = "heatmap") 
```

## SVM tuning
```{r}
set.seed(1234)
svm_tune <- tune.svm(x = label ~., 
                     data = new_train,
                     gamma = 10^(-3:3), 
                     cost = seq(1,10, by = 1),  
                     kernel = "radial")

svm_tune$best.parameters$gamma # 0.001
svm_tune$best.parameters$cost # 4
```
```{r}
set.seed(1234)
svm_tune <- tune.svm(x = label ~., 
                     data = new_train,
                     gamma = c(0.0001, 0.0005, 0.001, 0.005, 0.01, 0,05, 0.1, 0.5), 
                     cost = seq(3,5, by = 0.5),  
                     kernel = "radial")

svm_tune$best.parameters$gamma # 0.001
svm_tune$best.parameters$cost # 3.5
```

```{r}
set.seed(1234)
svm_model <- svm(formula = label~.,
                 data = new_train,
                 type = "C-classification",
                 kernel = "radial",
                 cross = 5,
                 gamma = svm_tune$best.parameters$gamma,
                 cost = svm_tune$best.parameters$cost,
                 probability = TRUE)
```

```{r}
model_svm <- new_test |>
  bind_cols(predict(svm_model, new_test))

cm_svm <- confusionMatrix(table(new_test$label, model_svm$...202)) 
cm_svm$byClass["F1"] # 0.7298578 
cm_svm$byClass["Precision"] # 0.7857143 
cm_svm$byClass["Recall"] # 0.6814159 
```
```{r}
new_test |>
  bind_cols(predict(svm_model, new_test)) |>
  conf_mat(truth = label, estimate = ...202) |>
  autoplot(type = "heatmap")
```

```{r}
test_preds <- predict(svm_model, new_test, probability = TRUE)
test_preds <- attr(test_preds, "probabilities")
test_preds <- test_preds |>
  as.data.frame() |>
  select(not_misinfo = "0", misinfo = "1")
```

```{r}
test_preds_df <- bind_cols(test, test_preds)
test_preds_df <- test_preds_df |>
  filter(not_misinfo > 0.9 | misinfo > 0.85)
```

```{r}
test_preds_df <- test_preds_df |>
  mutate(label = case_when(
    misinfo > 0.85 ~ "1",
    not_misinfo > 0.90 ~ "0"
  ))
```


# Recipe: logistic reg and gradient boosted trees

```{r}
model_recipe <- recipe(label~tweet, data = train) |>
  step_tokenize(tweet, engine = "spacyr") |>
  step_stopwords(tweet, language = "no", keep = FALSE, 
                 stopword_source = "snowball", 
                 custom_stopword_source = custom_words) |>
  step_lemma(tweet) |>
  step_word_embeddings(tweet, embeddings = no_we) |>
  step_normalize(all_numeric_predictors())

model_recipe
```

# Logistic regression
```{r}
lr_spec <- logistic_reg(penalty = tune(), mixture = 1) |>
  set_mode("classification") |>
  set_engine("glmnet")
```

```{r}
lr_workf <- workflow() |>
  add_model(lr_spec) |>
  add_recipe(model_recipe) 
lr_workf
```

```{r}
set.seed(8008)
folds <- vfold_cv(train, strata = label, v = 5, repeats = 2)
grid <- tibble(penalty = 10^seq(-3, 0, length.out = 20))
cls_metric <- metric_set(yardstick::precision, yardstick::recall, yardstick::f_meas)
```

```{r}
set.seed(1)
lr_res <- lr_workf |>
  tune_grid(resamples = folds, grid = grid, metrics = cls_metric)
```

```{r}
lr_params <- select_best(lr_res, metric = "f_meas")

lr_final_workf <- lr_workf |>
  finalize_workflow(lr_params)
```

```{r}
set.seed(2)
lr_final_fit <- fit(lr_final_workf, train)

lr_preds <- test |>
  bind_cols(predict(lr_final_fit, test))

cm_lr <- confusionMatrix(table(test$label, lr_preds$.pred_class)) 
cm_lr$byClass["F1"] # 0.7115385 
cm_lr$byClass["Precision"] # 0.755102 
cm_lr$byClass["Recall"] # 0.6727273 
```

```{r}
test |>
  bind_cols(predict(lr_final_fit, test)) |>
  conf_mat(truth = label, estimate = .pred_class) |> 
  autoplot(type = "heatmap") 
```
# Gradient Boosted Trees
```{r}
bt_spec <- boost_tree(trees = 500, min_n = tune(), tree_depth = tune(), loss_reduction = tune(), sample_size = tune(), mtry = tune()) |>
  set_mode("classification") |>
  set_engine("xgboost") 
```

```{r}
bt_workf <- workflow() |>
  add_model(bt_spec) |>
  add_recipe(model_recipe)
bt_workf
```
```{r}
set.seed(45)
folds <- vfold_cv(train, strata = label, v = 5, repeats = 2)
```

```{r}
grid <- grid_latin_hypercube(tree_depth(), 
                             min_n(), 
                             loss_reduction(), 
                             sample_size = sample_prop(), 
                             finalize(mtry(), train), 
                             size = 20)
grid
```


```{r}
set.seed(1)
bt_res <- bt_workf |>
  tune_grid(resamples = folds, grid = grid, control = control_grid(save_pred = TRUE), metrics = cls_metric)
```

```{r}
bt_params <- select_best(bt_res, metric = "f_meas")

bt_final_workf <- bt_workf |>
  finalize_workflow(bt_params)
```

```{r}
set.seed(2)
bt_final_fit <- fit(bt_final_workf, train)

bt_preds <- test |>
  bind_cols(predict(bt_final_fit, test))

cm_bt <- confusionMatrix(table(test$label, bt_preds$.pred_class)) 
cm_bt$byClass["F1"] # 0.6968974 
cm_bt$byClass["Precision"] # 0.744898 
cm_bt$byClass["Recall"] # 0.6547085 
```

```{r}
test |>
  bind_cols(predict(bt_final_fit, test)) |>
  conf_mat(truth = label, estimate = .pred_class) |>
  autoplot(type = "heatmap") 
```

